A meta-analysis of mental rotation ability in the first years of life

### 2022-05-01 code/analysis.Rmd
Make sensitivity analysis of `r_assumed` a table

    # Extract posterior draws
    tidy_draws(res_ri_sens) %>%
      mutate(ri_sens = ri_sens)
  }) -> draws_ri_sens

# Plot meta-analytic results for each assumed correlation
draws_ri_sens %>%
  mutate(ri_sens_f = fct_rev(factor(print_num(ri_sens)))) %>%
  ggplot(aes(y = ri_sens_f, x = b_Intercept)) +
  geom_vline(xintercept = seq(-0.75, 0.75, 0.25), color = "grey90") +
  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
  coord_cartesian(xlim = c(-0.75, 0.75), clip = "off") +
  scale_x_continuous(breaks = seq(-0.75, 0.75, 0.25)) +
  labs(x = expression("Hedges" ~ italic("g"))) +
  annotate(
    "text",
    label = "Correlation", x = -1.1, y = 7.86, hjust = 0,
    family = "Helvetica", fontface = "bold", color = "black"
  ) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(colour = "black"),
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_text(
      family = "Helvetica", color = "black", size = 3.88 * .pt,
      hjust = 0, vjust = -0.1, margin = margin(l = 20)
    ),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "ri_sens.pdf"), width = 4, height = 5)
```

>>>>

    # Compute ICC
    var_experiment_ri_sens <- as.matrix(
      res_ri_sens,
      variable = "sd_article:experiment__Intercept"
    )^2
    var_article_ri_sens <- as.matrix(
      res_ri_sens,
      variable = "sd_article__Intercept"
    )^2
    var_total_ri_sens <- var_experiment_ri_sens + var_article_ri_sens
    icc_ri_sens <- var_article_ri_sens / var_total_ri_sens
    icc_row <- mean_qi(icc_ri_sens) %>%
      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)

    # Extract summary statistics as a data frame row
    with(summary(res_ri_sens), bind_rows(fixed, bind_rows(random))) %>%
      bind_rows(icc_row) %>%
      transmute(
        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
      ) %>%
      pivot_wider(names_from = parameter, values_from = Estimate) %>%
      bind_cols(`Assumed r_i` = print_num(ri_sens), .)
  }) -> tab_ri_sens

# Save the table
write_csv(tab_ri_sens, file = here(tables_dir, "ri_sens.csv"))
```
